SPARQL on the Open, Decentralised Web

### 2016-07-25 dissertation/problems.tex
improve explanation of get_pattern etc

Until recently, a query engine would need to break down a SPARQL query
to individual triple pattern matches, which would then use for example
the \jcode{listStatements()} method of Jena, \jcode{filter()} method
of Sesame or \pcode{get\_statements} of \pmodule{RDF::Trine}, so that only
individual triple patterns could be evaluated against the underlying
triplestore.  The latter also had a \pcode{get\_pattern} method that
could be implemented if the underlying store had a way to optimise
Basic Graph Patterns. Sesame, on the other hand, allow implementations
to get a query representation, which it must then evaluate.
Nevertheless, this resulted in many problems:

@@

>>>>

Until recently, a query engine would need to break down a SPARQL query
to individual triple pattern matches, see
Section~\ref{sec:introinteract} for how frameworks tend to interact
with data. Typically, the query engine would then use for example
the \jcode{listStatements()} method of Jena, \jcode{filter()} method
of Sesame or \pcode{get\_statements} of \pmodule{RDF::Trine}, so that only
individual triple patterns could be evaluated against the underlying
triplestore.  The latter also had a \pcode{get\_pattern} method that
could be implemented if the underlying store had a way to optimise
Basic Graph Patterns. Sesame, on the other hand, allow implementations
to get a query representation, which it must then evaluate.
Nevertheless, this resulted in many problems:

@@

For example, an underlying SQL store could not compile one query for a
BGP, and could not use a \jcode{WHERE} clause to evaluate a SPARQL
\rdfterm{FILTER}. To remedy this, one could have a method for
evaluating BGPs with (such as the  \pcode{get\_pattern} method of
\pmodule{RDF::Trine}) and without filters, but:
